\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-08-12 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Complete first draft - Added Introduction, Application and Conclutions

	Have to explain why we are writing this
	\begin{itemize}
		\item Geometric intuition - restate existing results but with a new understanding.
		\item In particular champion projections.
		\item State that paper is in some ways a review paper.
		\item Propose a simple solution to the issue of bias.
	\end{itemize}

%	Large collections of time series often follow some aggregation structure. For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households. To ensure aligned decision making, it is important that forecasts at the most disaggregated level add up to forecasts at more aggregated levels. This property is called ``coherence''.  On the other hand ``reconciliation'' is a process whereby incoherent forecasts are made coherent. Both of these concepts have been developed extensively for point forecasting. Generalising both of these concepts, particularly the latter, to probabilistic forecasting is a gap that we seek to address in this work.  We do so by first providing a novel geometric interpretation to coherence and reconciliation in the point forecasting case. This can easily be generalised to probabilistic forecasting allowing us to derive further results for elliptical distributions as well as provide insight into forecast evaluation via multivariate  scoring rules. 
%	
%	Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level of the hierarchy. To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$ and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$. In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (series $AA$, $AB$, $BA$ and $BB$) and then summed to recover forecasts for all higher-level series. Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (series $Tot$) and bottom-level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions. A middle-out approach is a hybrid between these two, that for the hierarchy in Figure~\ref{fig1} would produce first stage forecasts for series $A$ and $B$.
%	
%	
%	In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular. For these methods, first stage forecasts are independently produced for all series rather than series at a single level. Since these so-called `base' forecasts are rarely coherent in practice, they are subsequently adjusted or `reconciled' to ensure coherence.  Note that we use coherence and reconciliation as distinct terms, in contrast to their at times ambiguous usage in the past. To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators. These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix. These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{AthEtAl2009,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
%	
%	A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \citep[see][and references therein]{Gneiting2014}. Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process. In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.
%	
%	To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections. In addition to being highly intuitive, this allows us to establish a number of theoretical results. We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections. We provide definitions of coherence and forecast reconciliation in the probabilistic setting, and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation. We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class. We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.
%	
%	We also cover the topic of forecast evaluation of probabilistic forecasts via scoring rules. In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts. Therefore we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts. Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.
%	
%	The remainder of the paper is structured as follows. In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts. Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results. In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules, while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian}. Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.

\section{Coherent forecasts}\label{sec:CoheForecasts}

@@

    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{Wickramasuriya2017}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.  A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables. We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$. The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.  The hierarchical structure of the data implies that the following holds for all $t$

@@

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.  Also notable by its absence in the above definition is any reference to {\em aggregation}. In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation. {\bf Include brief summary of all non-traditional hierarchies - e.g. grouped hierarchies, temporal hierarchies with wierd overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

@@

	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.  In general a projection matrix has the idemoptence property, i.e. $\bm{SG}^2=\bm{SG}$.  However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped onto itself by that projection. \todo{perhaps find a reference - it is so fundamental that is is on wikipedia and wolfram mathworld}  In our context this means that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.

@@

	The property that reconciliation should improve forecasts was touched upon in Section 2.3 of \cite{Wickramasuriya2017}.  The discussion in that paper focuses on the case of MinT. Here we provide a new explicit proof of that result first in the case of an orthogonal projection where the geometric intuition of the proof is clear and then generalise the result to reconciliation by any projection matrix in Section~\ref{sec:oblique}.

@@

	\begin{figure}[H]
		\centering
		\vspace{-0.9cm}
		\tiny
		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
		\label{fig:Schematic_OLSRecon}
		\caption{$\hat{\bm{y}}$ is orthogonally projected onto $\mathfrak{s}$}

@@

    Theorem~\ref{th:distred} is in some ways more powerful than perhaps previously understood.  Crucially, the result is not a result that requires taking expectations.  This distance reducing property will hold for any realisation and any forecast and not just on average.  Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made. \todo{include evidence from small empirical example.}

@@

	Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).  In contrast, \cite{Wickramasuriya2017} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.  The proof of \cite{Wickramasuriya2017} requires an assumptions about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.  The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.  As such the statement from \cite{Wickramasuriya2017} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true in with respect to a loss function that depends on ${\bm W}$.  If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts\todo{include empirical example}.

@@

	While the properties discussed so far hold for any projection matrix, the MinT method of \cite{Wickramasuriya2017} has an additional optimality property.  \cite{Wickramasuriya2017} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.  This choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.  Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.

	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection.  Imagining a similar oblique projection along $\bm{R}$ for all the grey points yield reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts.\todo{needs picture with all points projected obliquely then orthogonally}.    In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal is expectation.

@@

	\begin{figure}[H]
		\centering
		%\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\includegraphics{Figs/OrthProj.pdf}}
		\caption{\textcolor{red}{include caption}}\label{fig:Orthogonal_projection}
	\end{figure}

	\begin{figure}[H]
	\centering
	%\vspace{-0.9cm}
	\small
	\resizebox{\linewidth}{!}{
		\includegraphics{Figs/ObliqueProjection.pdf}}
	\caption{\textcolor{red}{include caption}}\label{fig:Oblique_projection}
	\end{figure}

@@

	\section{Bias in forecast reconciliation}

@@

	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation \cite{Wickramasuriya2017}.  Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.

@@

	\section{Bias correction}

	Our approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.  This can be then subtracted from future forecasts.  As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.  As such we see no problems with using the same errors to bias correct.  Geometrically, the intuition is simple.  In Figure~\ref{fig:MinT_justification1}, the orange points are centered around the origin as would be expected from an unbiased forecast.  If forecasts are biased, then errors should simply be translated until they are centered at the origin.

	\section{Application}

	\section{Conclusions}

	\newpage

>>>>

	A collection of multiple time series with some aggregation structure arises in many disciplines such as manufacturing, engineering, marketing, medicine, etc. These are often known as hierarchical time series. Making coherent forecasts for these series that are in line with the inherent aggregation constraints is an essential requirement for decision making. Early studies on this literature use a single level forecasting approaches. That is, forecasting the series in a single level of the hierarchy and then aggregate or disaggregate these forecasts to get coherent forecasts for remaining series. The well known Bottom-up \citep{Dunn1976} and Top-down \citep{Gross1990, Athanasopoulos2009} methods are examples for these traditional methods. Multiple studies also discuss the relative advantages and disadvantages of these methods, for example, \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.

	A shortcoming of these traditional methods is that they do not use all the information available in the hierarchy to make coherent forecasts. To overcome this issue, \cite{Hyndman2011} propose to utilise all the information available in the hierarchy via a ``Reconciliation" process. This is a two-stages process where the first stage involves making forecasts for all series in the hierarchy without considering the aggregation constraints (also known as base forecasts), which is then followed by the reconciliation stage that combines these forecasts imposing the aggregation constraints of the hierarchy. A later study by \cite{WicEtAl2019} proposed to optimally combine the base forecasts by minimising the trace of the mean squared errors of reconciled forecasts where they derived an analytical solution to produce reconciled forecasts. An important feature of this method is that it imposes the correlation structure of the whole hierarchy to produce reconciled point forecasts.

	While reviewing the existing studies in this literature, our attempt is to give a new understanding to the whole hierarchical forecasting problem with a geometric intuition. We first provide a geometric interpretation of coherency and reconciliation in terms of projections. Then we rehash all existing reconciliation methods into a single framework based on projections. In addition to being highly intuitive, this allows us to establish new theoretical results. We prove two new theorems about point forecast reconciliation, the first showing that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections while the second shows that reconciliation via projections preserves the unbiasedness of base forecasts.

	Unbiasedness of base forecasts is a strong assumption in many of the existing methods which will be limited only to a selective number of forecasting methods. We propose a simple solution to this barrier. That is to correct the bias in base forecasts before doing the projection-based reconciliation. This allows using any advanced statistical method despite the unbiasedness to produce base forecasts without worrying about the unbiasedness. Using an empirical study, we further show that the reconciled forecasts follow from biased corrected base forecasts will improve the forecast accuracy compared to that of the biased forecasts.

	The remainder of this paper is structured as follows. In Section~\ref{sec:CoheForecasts} coherent point forecasting is defined geometrically while section~\ref{sec:Reconciliation} contains definitions of projection-based reconciliation as well as our main theoretical results. Section~\ref{sec:BiasInRecon} discuss the unbiased preserving property of projection-based reconciliation and Section \ref{sec:BiasCorrection} contains our proposed method to correct the bias in base forecasts. In Section \ref{sec:EmpStudy} we apply these methods to get coherent forecasts for domestic tourism flow in Australia and Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.  
\section{Coherent forecasts}\label{sec:CoheForecasts}

@@

    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{WicEtAl2019}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.  A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables. We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$. The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.  The hierarchical structure of the data implies that the following holds for all $t$

@@

	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.  Also notable by its absence in the above definition is any reference to {\em aggregation}. In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation. {\bf Include brief summary of all non-traditional hierarchies - e.g. grouped hierarchies, temporal hierarchies with weird overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.

@@

	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.  In general a projection matrix has the idemoptence property, i.e. $\bm{SG}^2=\bm{SG}$.  However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped onto itself by that projection. This is a fundamental property of projections and also proved in lemma 2.4 in \citet{rao1974}. In our context this means that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.

@@

	The property that reconciliation should improve forecasts was touched upon in Section 2.3 of \cite{WicEtAl2019}.  The discussion in that paper focuses on the case of MinT. Here we provide a new explicit proof of that result first in the case of an orthogonal projection where the geometric intuition of the proof is clear and then generalise the result to reconciliation by any projection matrix in Section~\ref{sec:oblique}.

@@

	\begin{figure}[H]\label{fig:Schematic_OLSRecon}
		\centering
		\vspace{-0.9cm}
		\tiny
		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
		\caption{$\hat{\bm{y}}$ is orthogonally projected onto $\mathfrak{s}$}

@@

    Theorem~\ref{th:distred} is in some ways more powerful than perhaps previously understood.  Crucially, the result is not a result that requires taking expectations.  This distance reducing property will hold for any realisation and any forecast and not just on average.  Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.

@@

	Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).  In contrast, \cite{WicEtAl2019} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.  The proof of \cite{WicEtAl2019} requires an assumptions about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.  The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.  As such the statement from \cite{WicEtAl2019} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true in with respect to a loss function that depends on ${\bm W}$.  If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.

@@

	While the properties discussed so far hold for any projection matrix, the MinT method of \cite{WicEtAl2019} has an additional optimality property.  \cite{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.  This choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.  Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.

	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection showed as in Figure \ref{fig:Orthogonal_projection_all_points}.  Figure \ref{fig:Oblique_projection_all_points} depicts a similar oblique projection along $\bm{R}$ for all the gray points yield reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts. In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal is expectation.

@@

	\begin{figure}[H]
		\centering
		%\vspace{-0.9cm}
		\small
		\resizebox{\linewidth}{!}{
			\includegraphics{Figs/OrthProj.pdf}}
		\caption{All gray points are orthogonally projected onto the coherent subspace $\mathfrak{s}$. Reconciled forecasts marked in red dots are widely spread about the target $\bm{y}$.}\label{fig:Orthogonal_projection_all_points}
	\end{figure}

	\begin{figure}[H] 
	\centering
	%\vspace{-0.9cm}
	\small
	\resizebox{\linewidth}{!}{
		\includegraphics{Figs/ObliqueProjection.pdf}}
	\caption{All gray points are obliquely projected along the direction of $\bm{R}$. Reconciled points denoted in red dots are concentrated about the target $\bm{y}$.}\label{fig:Oblique_projection_all_points}
	\end{figure}

@@

	\section{Bias in forecast reconciliation}\label{sec:BiasInRecon}

@@

	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation \cite{WicEtAl2019}.  Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.

@@

	\section{Bias correction} \label{sec:BiasCorrection}
	\todo{Need to discuss and rewrite this section since we are using different bias correction method in the empirical study}
	Our approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.  This can be then subtracted from future forecasts.  As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.  As such we see no problems with using the same errors to bias correct.  Geometrically, the intuition is simple.  In Figure~\ref{fig:MinT_justification1}, the orange points are centered around the origin as would be expected from an unbiased forecast.  If forecasts are biased, then errors should simply be translated until they are centered at the origin.

	\section{Empirical study} \label{sec:EmpStudy}

	Total tourism flow of any country can naturally disaggregate along a geographical hierarchy. Producing accurate forecasts for these hierarchical time series while preserving the coherency is important for making align business decisions in the tourism industry. Many applications related to Australian tourism flow have pronounced that reconciliation improves the point forecast accuracy (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}).

	Using a similar empirical application to tourism forecasting in Australia, we show how to use projection-based reconciliation when we have a set of biased incoherent forecasts. As we mentioned in the previous section our focus is to bias adjust the incoherent forecasts first and then do the reconciliation.

	\subsubsection*{Data:}
	We use ``overnight trips" as a measure of domestic tourism flow in Australia. Total ``overnight trips" in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a geographical hierarchy with $110$ total number of series and $75$ bottom level series. More information about the series of this hierarchy is given in Table \ref{table:A1} in the appendix. Data were obtained from the National Visitor Survey (NVS) which were collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more. Data form a monthly series starting from January 1998 to December 2017 which gives a total of $240$ observations per series.

	We produce $h=1$ to $h=6$ months ahead forecasts using a rolling window approach. First training window of $100$ observations is considered from Jan-$1998$ to Apr-$2006$ and produce forecasts for May-$2006$ to Oct-$2006$. Then we roll the training window one month at a time where the final forecast is produced for Dec-$2017$. This directs to $140 \quad 1$-step-ahead, $139 \quad 2$-step-ahead through $135 \quad 6$-step-ahead forecasts left for evaluation.

	\subsubsection*{Preliminary analysis:}

	While observing the patterns of individual series, we noticed that the signal-to-noise ratio decreases with the disaggregate level of the hierarchy. From Figure \ref{fig:Total_TSplots} and \ref{fig:States_Zones_Regs_TSplots} this is depicted well as we see much noisier series in bottom levels whereas the noise level is comparatively stabilised in the upper levels. We have also observed that the overnight trips for `Adelaide Hills` has an anomalous observation on December-2002. We replaced this observation with the average overnight trips on December-2001 and December-2003 for the same destination.

	\begin{figure}
		\centering
		\small
		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplot.pdf}
		\caption{Time plot for total overnight trips.}\label{fig:Total_TSplots}
	\end{figure}

	\begin{figure}
		\centering
		\small
		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots.pdf}
		\caption{Time plot for some selected series from different disaggregate levels of the hierarchy.}\label{fig:States_Zones_Regs_TSplots}
	\end{figure}

	\subsubsection*{Base forecasts and reconciliation:}

	We first transform each series in the hierarchy using the Box-Cox transformation as given in equation (\ref{eq:BoxCox_transformation}) to stabilise any variations in the data.

	\begin{equation} \label{eq:BoxCox_transformation}
	x_t = 
	\begin{cases} 
	\log(y_t) & \text{if } \lambda = 0 \\
	\frac{y_t^\lambda - 1}{\lambda}  & \text{if } \lambda \ne 0
	\end{cases}
	\end{equation}

	We use "guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package R software \citep{Rforecast} to select optimal $\lambda$. Then  we fit univariate ARIMA models for the transformed series. We use \verb|auto.arima()| function in \verb|forecast| package to choose the best model that minimises the AIC. Using the fitted models we produce $h=1,...,6$ months ahead forecasts for each series in the hierarchy. These forecasts are then back-transformed using equation (\ref{eq:BoxCox_back-transformation}) to scale them back into the original space. However, the back transformed forecasts will be biased \citep{FPP2018}.

	\begin{equation} \label{eq:BoxCox_back-transformation}
	y_{t+h} = 
	\begin{cases} 
	\exp({x_{t+h}}) & \text{if } \lambda = 0 \\
	(\lambda x_{t+h} + 1)^{1/\lambda}  & \text{if } \lambda \ne 0
	\end{cases}
	\end{equation}

	Hence the reconciled forecasts follow from these will also biased. This is the exact scenario that we want to demonstrate in this study. As we proposed before, we first bias correct the base forecasts prior to the reconciliation. We use the mathematical formula in equation (\ref{eq:BoxCox_BT_biasadj}) to calculate the back-transformed and bias-adjusted forecasts.

	\begin{equation} \label{eq:BoxCox_BT_biasadj}
	 y_{t+h} = 
	\begin{cases} 
	\exp({x_{t+h}})[1+\frac{\sigma_h^2}{2}] & \text{if } \lambda = 0 \\
	(\lambda x_{t+h} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda x_{t+h} + 1)^2}]       & \text{if } \lambda \ne 0
	\end{cases}
	\end{equation}
	where, $x_{t+h}$ is the $h$-step-ahead forecasts from the Box-Cox transformed series and $\sigma_h^2$ is the variance of $x_{t+h}$.

	Once we get the base forecasts for all series in the hierarchy, we can do the projection-based reconciliation to get coherent forecasts. We reconcile both biased and bias-corrected (unbiased) base forecasts to demonstrate how the reconciliation follows from unbiased base forecasts improves the forecast accuracy. MinT(Shrink), WLS, OLS and bottom-up methods are used for reconciliation.

	\subsubsection*{Results and discussion:}

	Mean Squared Error (MSE) is used to measure the forecast accuracy and results are presented in Table \ref{tab:Results_MSE}. Recall that projections preserve the unbiasedness in reconciled forecasts only if the base forecasts are unbiased. As a consequence, the reconciled forecasts follow from the biased base forecasts will also be biased. We can see from the results that unbiased-reconciled forecasts from MinT(Shrink) and WLS are better than that of biased-reconciled forecasts although the unbiased-base forecasts are not necessarily better than the biased-base forecasts. Furthermore, unbiased MinT reconciled forecasts are outperforming all biased and unbiased forecasts. These results are true for all forecast horizons.

	\begin{table}
		\caption {Average {MSE($\times 10^3$)} of base and reconciled point forecasts at forecasts horizons $h=1,...,6$ are presented. Bias and unbiased columns represent the results for biased-base/biased-reconciled and unbiased-base/unbiased-reconciled forecasts respectively. Comparisons can be made across biased vs unbiased forecasts as well as base vs reconciled forecasts.}
		\label{tab:Results_MSE}
		\centering\tabcolsep=0.08cm

		\resizebox{\linewidth}{!}{
		\begin{tabular}{@{}lSSSSSSSSSSSS@{}}
			\toprule
			\multicolumn{1}{c}{ } & \multicolumn{2}{c}{h=1} & \multicolumn{2}{c}{h=2} & \multicolumn{2}{c}{h=3} & \multicolumn{2}{c}{h=4} & \multicolumn{2}{c}{h=5} & \multicolumn{2}{c}{h=6} \\
			\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13}
			Method & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased\\
			\midrule
			Base & 12.18 & 161.63 & 13.14 & 243.13 & 14.08 & 269.20 & 15.88 & 325.41 & 15.49 & 332.11 & 15.79 & 344.40\\
			\hline
			MinT(Shrink) & 10.14 & $\bm{9.96}$ & 11.47 & $\bm{10.78}$ & 12.55 & $\bm{11.94}$ & 15.53 & $\bm{14.03}$ & 14.63 & $\bm{13.46}$ & 15.28 & $\bm{13.78}$\\
			\hline
			WLS & 15.62 & 13.97 & 15.93 & 13.71 & 16.65 & 14.50 & 18.91 & 16.26 & 18.76 & 16.20 & 18.85 & 15.83\\	
			\hline
			OLS & 11.73 & 135.17 & 12.80 & 204.42 & 13.73 & 225.59 & 15.56 & 272.41 & 15.17 & 278.08 & 15.49 & 288.21\\
			\hline
			Bottom-up & 17.86 & 15.55 & 17.86 & 14.90 & 18.47 & 15.61 & 20.50 & 17.21 & 20.34 & 17.04 & 20.39 & 16.69\\

			\bottomrule
		\end{tabular}
	}
	\end{table}

%	\begin{figure}
%		\centering
%		\small
%		\includegraphics[width = \textwidth]{Empirical-results/Final-results/SS_MSE_Results.pdf}
%		\caption{\textcolor{red}{include caption}}\label{fig:MSE_SkillScore}
%	\end{figure}
%

	Following the distance reducing property in Theorem \ref{th:distred} and the discussion therein, we have noted that the orthogonal projections will always improve the base forecasts with respect to the mean squared errors whereas, the oblique projections will not always, but improves only on average. Figure \ref{fig:BaseVSRecon_Fc} shows the MSE difference between base forecasts and reconciled forecasts - MinT, OLS and WLS for all replications in different forecast horizons. Recall that OLS reconciliation is doing orthogonal projection whereas MinT and WLS are doing oblique projections onto the coherent subspace. It is apparent from the plot that the MSE difference for OLS is always positive, implying that OLS improves the base in terms of MSE in all replications. On the other hand,  there are some instances that this difference for MinT and WLS is negative which is reflected from the short negative tails of box-plots. This implies that oblique projections will not improve the base forecasts in every case. However, these projections will outperform the base with respect to MSE on average which is again reflected from the highly positive skewed MSE differences.

	 \begin{figure}[H]
		\centering
		\small
		\includegraphics[width = \textwidth]{Empirical-results/Final-results/Base-Recon.pdf}
		\caption{Difference of MSE between Base forecasts and reconciled forecasts over the replications in distinct forecast horizons. Positive values of the difference implies reconciliation improves the forecast accuracy than base forecasts.}\label{fig:BaseVSRecon_Fc}
	\end{figure}

	\section{Conclusions} \label{sec:conclusions}

	By redefining coherent point forecast and point forecast reconciliation, we rehash all existing reconciliation methods into a single projection based geometric framework. We have also established new theoretical results that support the use of projections for point forecast reconciliation. We show that projection of unbiased base forecasts onto the coherent subspace will always produce unbiased reconciled forecasts. Yet the projection-based reconciliation can be used to reconciled bias base forecasts after bias adjustments. Empirical results from the application of these methods to forecasting Australian domestic tourism flow show that reconciled forecast follows from bias-adjusted base improves the forecast accuracy and unbiased MinT reconciliation is outperforming.

	These new geometric interpretations of hierarchical forecast reconciliation facilitate extensions of the problem to a probabilistic framework. We leave this discussion into a different paper. 	
	\newpage
	\section{Appendix}

	\begin{table} 
		\caption{Geographical hierarchy of Australian tourism flow}\label{table:A1}
